Minimal trap-spaces of Logical models are maximal siphons of their Petri net encoding

### 2022-05-04 cmsb22.tex
Update the result table, update Section "Answer set programming-based method", update Section "Preliminaries"

\subsection{Traps-spaces}

We recall here some definitions from~\cite{klarner2015computing} for the introduction of \emph{trap-spaces}.
Minimal trap-spaces prove to be a very good approximation of the attractors of a Boolean model and have become the \emph{de facto} standard way to analyze models of a few tens of \emph{genes}~\cite{klarner2017pyboolnet,cifuentes2020control}.

Given a Boolean model \(\mathcal{M} = (V, F)\) with variables \(V=(v_{1},\dots,v_{n})\) and Boolean functions \(F=(f_{1},\dots,f_{n})\), its state-space is \(\mathcal{S}_{\mathcal{M}} =\bbbb^{n}\) with \(\bbbb = \{0, 1\}\).

@@

\sylvain{missing example?}

@@

  A \emph{Petri net graph} is a weighted bipartite directed graph \((P, T, W)\),
  where \(P\) is a non-empty finite set of vertices called \emph{places},
  \(T\) is a non-empty finite set of vertices called \emph{transitions},
  \(P \cap T = \emptyset\),
  and \(W : (P \times T) \cup (T \times P) \mapsto \bbbn \) is a weight function attached to the arcs.

@@

We will write \(pred(x)\) (resp.\ \(succ(x)\)) to represent the set of vertices that have an (non-zero weighted) arc leading to (resp.\ coming from) \(x\).

@@

Since our study is focused on Boolean models, we briefly recall the original encoding here.
Its basis is that every \emph{gene} of the original model is represented by two separate places (\(p\) and \(\overline{p}\)), corresponding to its two states, active, and inactive.
Each conjunct of the logical function that activate the \emph{gene} will lead to a transition, consuming the inactive place, producing the active place, and with all other literals both consumed and produced.
And conversely for the inactivation.

@@

  First, we show that if \(m\) is a trap space of \(\mathcal{M}\), then \(S\) is a conflict-free siphon of \(\mathcal{P}\) (*). If \(D_m = \emptyset\), then \(S = \emptyset\) is trivially a conflict-free siphon of \(\mathcal{P}\). Thus, we consider the case that \(D_m \neq \emptyset\) (resp. \(S \neq \emptyset\)). Assume that \(S\) is not a siphon of \(\mathcal{P}\). Then, there is a transition \(t \in T\) such that \(S\cap succ(t)\not =\emptyset\) but \(S\cap pred(t)\not =\emptyset\). In other words, there is a place \(p \in S\) such that \(p \in succ(t)\) but \(p \not \in pred(t)\). Let \(v\) be the corresponding node in \(\mathcal{M}\) of \(p\). By the characterization of the encoding~\cite{chatain2014characterization}, there is a directional arc from \(t\) to \(p\) and a directional arc from the complementary place of \(p\) to \(t\). Without loss of generality, we assume that \(p = p_v\), then there is a directional arc from \(t\) to \(p_v\) and a directional arc from \(\overline{p}_v\) to \(t\). In addition, there is also no arc or a bi-directional arc between \(t\) and another place rather than \(p_v\) and \(\overline{p}_v\). Thus, there is no connecting arc between \(t\) and any place in \(S \setminus \{p_v\}\) because \(S\cap pred(t)\not =\emptyset\). In \(\mathcal{S}_{\mathcal{M}}[m]\), a node in \(V \setminus D_m\) can receive any Boolean value. Hence, there is a state \(s \in \mathcal{S}_{\mathcal{M}}[m]\) such that \(m_s(p') = 1, \forall p' \in pred(t) \setminus \{\overline{p_v}\}\) where \(m_s\) is the corresponding marking in \(\mathcal{P}\) of \(s\). We also have \(m_s(p_v) = 0\), leading to \(m_s(\overline{p_v}) = 1\) by the characterization of the encoding~\cite{chatain2014characterization}. Now, \(t\) is enabled at marking \(m_s\). Its firing leads to a new marking \(m'_s\) such that \(m'_s(p_v) = 1\) and \(m'_s(\overline{p}_v) = 0\). Let \(s'\) be the corresponding state in \(\mathcal{M}\) of \(m'_s\). Since \(m\) is a trap space of \(\mathcal{M}\), \(s' \in \mathcal{S}_{\mathcal{M}}[m]\). Then, \(s'(v) = m(v)\), leading to \(m'_s(p_v) = 0\), which is a contradiction. Hence, \(S\) is a siphon of \(\mathcal{P}\). By the definition of a mirror, \(S\) is also a conflict-free one.

  Second, we show that if \(S\) is a conflict-free siphon of \(\mathcal{P}\), then \(m\) is a trap space of \(\mathcal{M}\) (**). By the definition of a mirror, \(m\) is a subspace of \(\mathcal{M}\). Let \(s\) be an arbitrary state in \(\mathcal{S}_{\mathcal{M}}[m]\) and \(m_s\) be its corresponding marking in \(\mathcal{P}\). By the characterization of the encoding~\cite{chatain2014characterization}, \(m_s(p) = 0, \forall p \in S\). In any marking \(m'_s\) reachable from \(m_s\) regardless of the update semantics of \(\mathcal{P}\), we have \(m'_s(p) = 0, \forall p \in S\) by the characterization of a siphon~\cite{DBLP:journals/isci/LiuB16}. Equivalently, in any state \(s'\) reachable from \(s\) regardless of the update semantics of \(\mathcal{M}\), we have \(s'(v) = s(v) = m(v), \forall v \in D_m\). Then, \(s' \in \mathcal{S}_{\mathcal{M}}[m]\). By the definition of a trap space and the arbitrariness of \(s\), \(m\) is a trap space of \(\mathcal{M}\).

@@

\section{Answer set programming-based method}

ASP

\section{Evaluation}
To assess the efficiency of the proposed method, we compared it with the state-of-the-art method PyBoolNet~\cite{klarner2017pyboolnet}.
We used a set of real-world Boolean models lying in various scales obtained from the literature.
These models are quite big (in size), complex (i.e., having high average in-degree, which is related to the number of prime-implicants) and most of them have never been fully analyzed.
We then applied the proposed method and PyBoolNet to computing minimal trap spaces of these real-world models.
To solve the ASP problems, we used the same ASP solver CLINGO~\cite{DBLP:journals/aicom/GebserKKOSS11} and the same configuration as that used in PyBoolNet~\cite{klarner2015computing}.
Specifically, we used the configuration \texttt{--dom-pref=32, --heu=domain, --dom-mod=7} (subset maximality). We ran all the benchmarks on a virtual machine whose environment is CPU: Intel(R) Core(TM) i7-3630QM 2.40GHz x 4, Memory: 8 GB, Ubuntu 18.04.2 64 bit. Finally, we set a time limit as one hour for each model.

\sylvain{we need a source for the models as much as possible, or to refer to some place where people can access them to reproduce the benchmark.}
\vangiang{Yes. I have added reference sources for the models but some models are still missing now.}

@@

\begin{table}[!ht]
  \caption{Timing comparisons between the proposed method and PyBoolNet on the selected real-world models.
    Columns "\(n\)", "\(e\)", and "\(s\)" denote the numbers of nodes, interactions, and source nodes of each model, respectively. For each method, Column "\(|M|\)" denotes the number of minimal trap spaces and Column "time (s)" denotes the computation time in seconds.
    "DNF" means that the method did not finish the computation within one hour.}
  \centering
  \label{tab:result_real}
  \begin{tabular}{lrrrrrrr}
    \toprule
    & & & & \multicolumn{2}{c}{PyBoolNet} & \multicolumn{2}{c}{Proposed method}\\
    \cmidrule(lr){5-6}\cmidrule(lr){7-8}
    model & $n$ & $e$ & $s$ & $|M|$ & time (s) & $|M|$ & time (s) \\ \midrule
    inflammatory-bowel-disease~\cite{DBLP:journals/bmcsb/HelikarKMBRMWSLR12} & 47 & 287 & 0 & DNF & DNF & 1 & 296.23 \\
    T-LGL-survival-network-2008~\cite{DBLP:journals/bmcsb/HelikarKMBRMWSLR12} & 61 & 193 & 7 & - & - & 318 & 0.24 \\
    butanol-production~\cite{DBLP:journals/bmcsb/HelikarKMBRMWSLR12} & 66 & 139 & 13 & - & - & 512 & 0.17 \\
    colitis-associated-colon-cancer~\cite{DBLP:journals/bmcsb/HelikarKMBRMWSLR12} & 70 & 153 & 1 & - & - & 10 & 0.18 \\
    IL-6-signalling~\cite{DBLP:journals/bmcsb/HelikarKMBRMWSLR12} & 86 & 149 & 15 & - & - & 512 & 0.32 \\
    Corral-ThIL-17-diff~\cite{corral2021interplay} & 92 & - & 16 & - & - & 5724 & 0.90 \\
    Korkut-2015~\cite{lee2019signal} & 99 & - & 12 & DNF & DNF & 2060 & 2.86 \\ \midrule

    adhesion-cip-migration-cell-cycle~\cite{guberman2020boolean} & 121 & 493 & - & - & - & 78 & 3.72 \\
    interferon-1~\cite{ostaszewski2021covid19} & 121 & 190 & 55 & - & - & 512 & 0.43 \\
    TCR-TLR5-signaling-2018~\cite{rodriguez2019cooperation} & 130 & 273 & 2 & - & - & 48 & 0.50 \\
    influenza-virus-replication-cycle~\cite{DBLP:journals/bmcsb/HelikarKMBRMWSLR12} & 131 & 302 & 11 & - & - & 2560 & 1.07 \\
    signaling-in-prostate-cancer~\cite{Montagud2021} & 133 & 431 & 0 & - & - & 812 & 1.40 \\
    HIV-1-with-T-cell-signaling~\cite{DBLP:journals/bmcsb/HelikarKMBRMWSLR12} & 138 & 368 & 14 & DNF & DNF & 1408 & 1.44 \\
    signal-transduction-in-fibroblasts~\cite{helikar2008emergent} & 139 & 557 & 9 & - & - & 375850 & 331.87 \\
    HMOX-1-pathway~\cite{ostaszewski2021covid19} & 145 & 228 & 56 & - & - & 5120 & 0.99 \\
    kynurenine-pathway~\cite{ostaszewski2021covid19} & 150 & 304 & 72 & - & - & 512 & 3.79 \\
    virus-replication-cycle~\cite{ostaszewski2021covid19} & 154 & 268 & 25 & - & - & 1024 & 0.67 \\
    immune-system~\cite{DBLP:journals/bmcsb/HelikarKMBRMWSLR12} & 164 & 506 & 13 & DNF & DNF & 36852 & 14.19 \\
    er-stress~\cite{ostaszewski2021covid19} & 182 & 266 & 75 & - & - & 25600 & 4.54 \\
    cascade-3~\cite{Tsirvouli2020} & 183 & 603 & 0 & - & - & 1 & 1.65 \\
    CHO-2016~\cite{lee2019signal} & 200 & 696 & 13 & - & - & 1024 & 2.10 \\ \midrule

>>>>

\subsection{Traps spaces}

We recall here some definitions from~\cite{klarner2015computing} for the introduction of \emph{trap spaces}.
Minimal trap-spaces prove to be a very good approximation of the attractors of a Boolean model and have become the \emph{de facto} standard way to analyze models of a few tens of \emph{genes}~\cite{klarner2017pyboolnet,cifuentes2020control}.

%%% Trap set %%%
Given a Boolean model \(\mathcal{M} = (V, F)\) with variables \(V=(v_{1},\dots,v_{n})\) and Boolean functions \(F=(f_{1},\dots,f_{n})\), its state-space is \(\mathcal{S}_{\mathcal{M}} =\bbbb^{n}\) with \(\bbbb = \{0, 1\}\). A non-empty set \(T \subseteq S_{\mathcal{M}}\) is a \emph{trap set} of \(\mathcal{M}\) if and only if for every \(x \in T\) and \(y \in S_{\mathcal{M}}\) with \(y\) is reachable from \(x\) it holds that \(y \in T\).

@@

%%% Example %%%
\begin{example}
We give a BN \(\mathcal{N} = (V, F)\), where \(V = \{x_1, x_2\}\) and \(F = \{f_1, f_2\}\) with \(f_1 = (x_1 \land x_2) \lor (\neg x_1 \land \neg x_2), f_2 = (x_1 \land x_2) \lor (\neg x_1 \land \neg x_2)\). Herein, \(\land\), \(\lor\), and \(\neg\) denote the CONJUNCTION, DISJUNCTION, and NEGATION logical operators, respectively.
\label{example:BN}
\end{example}

%\sylvain{missing example?}

@@

  A \emph{Petri net} is a weighted bipartite directed graph \((P, T, W)\),
  where \(P\) is a non-empty finite set of vertices called \emph{places},
  \(T\) is a non-empty finite set of vertices called \emph{transitions},
  \(P \cap T = \emptyset\),
  and \(W : (P \times T) \cup (T \times P) \mapsto \bbbn \) is a weight function attached to the arcs.

@@

We shall write \(pred(x)\) (resp.\ \(succ(x)\)) to represent the set of vertices that have an (non-zero weighted) arc leading to (resp.\ coming from) \(x\).

@@

Since our study is focused on Boolean models, we briefly recall the original encoding here.
Its basis is that every node (\emph{gene}) \(v\) of the original model is represented by two separate places (\(p_v\) and \(\overline{p}_v\)), corresponding to its two states, active, and inactive, respectively.
Each conjunct of the logical function that activate the \emph{gene} will lead to a transition \(t\), consuming the inactive place (i.e., a directional arc from \(\overline{p}_v\) to \(t\)), producing the active place (i.e., a directional arc from \(t\) to \(p_v\)), and with all other literals both consumed and produced (i.e., a bi-directional arc).
And conversely for the inactivation. 
Let \(s\) be a state of the Boolean model and \(m_s\) be its the corresponding marking in the encoded Petri net. It holds that \(\forall v \in V\), \(s(v) = 0\) if and only if \(m_s(\overline{p}_v) = 1\) and \(s(v) = 1\) if and only if \(m_s(p_v) = 1\).

@@

  First, we show that if \(m\) is a trap space of \(\mathcal{M}\), then \(S\) is a conflict-free siphon of \(\mathcal{P}\) (*). If \(D_m = \emptyset\), then \(S = \emptyset\) is trivially a conflict-free siphon of \(\mathcal{P}\). Thus, we consider the case that \(D_m \neq \emptyset\) (resp. \(S \neq \emptyset\)). Assume that \(S\) is not a siphon of \(\mathcal{P}\). Then, there is a transition \(t \in T\) such that \(S\cap succ(t)\not =\emptyset\) but \(S\cap pred(t)\not =\emptyset\). In other words, there is a place \(p \in S\) such that \(p \in succ(t)\) but \(p \not \in pred(t)\). Let \(v\) be the corresponding node in \(\mathcal{M}\) of \(p\). By the characterization of the encoding~\cite{chaouiya2004qualitative}, there is a directional arc from \(t\) to \(p\) and a directional arc from the complementary place of \(p\) to \(t\). Without loss of generality, we assume that \(p = p_v\), then there is a directional arc from \(t\) to \(p_v\) and a directional arc from \(\overline{p}_v\) to \(t\). In addition, there is also no arc or a bi-directional arc between \(t\) and another place rather than \(p_v\) and \(\overline{p}_v\). Thus, there is no connecting arc between \(t\) and any place in \(S \setminus \{p_v\}\) because \(S\cap pred(t)\not =\emptyset\). In \(\mathcal{S}_{\mathcal{M}}[m]\), a node in \(V \setminus D_m\) can receive any Boolean value. Hence, there is a state \(s \in \mathcal{S}_{\mathcal{M}}[m]\) such that \(m_s(p') = 1, \forall p' \in pred(t) \setminus \{\overline{p_v}\}\) where \(m_s\) is the corresponding marking in \(\mathcal{P}\) of \(s\). We also have \(m_s(p_v) = 0\), leading to \(m_s(\overline{p_v}) = 1\) by the characterization of the encoding~\cite{chaouiya2004qualitative}. Now, \(t\) is enabled at marking \(m_s\). Its firing leads to a new marking \(m'_s\) such that \(m'_s(p_v) = 1\) and \(m'_s(\overline{p}_v) = 0\). Let \(s'\) be the corresponding state in \(\mathcal{M}\) of \(m'_s\). Since \(m\) is a trap space of \(\mathcal{M}\), \(s' \in \mathcal{S}_{\mathcal{M}}[m]\). Then, \(s'(v) = m(v)\), leading to \(m'_s(p_v) = 0\), which is a contradiction. Hence, \(S\) is a siphon of \(\mathcal{P}\). By the definition of a mirror, \(S\) is also a conflict-free one.

  Second, we show that if \(S\) is a conflict-free siphon of \(\mathcal{P}\), then \(m\) is a trap space of \(\mathcal{M}\) (**). By the definition of a mirror, \(m\) is a subspace of \(\mathcal{M}\). Let \(s\) be an arbitrary state in \(\mathcal{S}_{\mathcal{M}}[m]\) and \(m_s\) be its corresponding marking in \(\mathcal{P}\). By the characterization of the encoding~\cite{chaouiya2004qualitative}, \(m_s(p) = 0, \forall p \in S\). In any marking \(m'_s\) reachable from \(m_s\) regardless of the update semantics of \(\mathcal{P}\), we have \(m'_s(p) = 0, \forall p \in S\) by the characterization of a siphon~\cite{DBLP:journals/isci/LiuB16}. Equivalently, in any state \(s'\) reachable from \(s\) regardless of the update semantics of \(\mathcal{M}\), we have \(s'(v) = s(v) = m(v), \forall v \in D_m\). Then, \(s' \in \mathcal{S}_{\mathcal{M}}[m]\). By the definition of a trap space and the arbitrariness of \(s\), \(m\) is a trap space of \(\mathcal{M}\).

@@

\section{Answer set programming-based method}
First, we show the characterization of a conflict-free siphon of the encoded Petri net \(\mathcal{P}\). ...

Then, we translate the above characterization into the ASP \(\mathcal{A}\) as follows. We use atom \texttt{p(v, 1)} (resp. \texttt{p(v, 0)}) to denote place \(p_v\) (resp. \(\overline{p_v}\)), \(\forall v \in V\). The constraint (C2) is translated to the rule
\[\verb|:- p(v, 1), p(v, 0).|\]
for each \(v \in V\). ...

Naturally, a stable model \(A\) of \(\mathcal{A}\) is equivalent to a conflict-free siphon \(S\) of \(\mathcal{P}\), thus a minimal trap space \(m\) of \(\mathcal{M}\). The conversion from \(A\) to \(m\) is straightforward. If \(\texttt{p(v, 1)} \in A\) then \(v \in D_m\) and \(m(v) = 0\). Conversely, if \(\texttt{p(v, 0)} \in A\) then \(v \in D_m\) and \(m(v) = 1\). Otherwise, \(v \not \in D_m\). Computing multiple solutions is built into ASP solvers and the solving collection POTASSCO~\cite{DBLP:journals/aicom/GebserKKOSS11} also features the option to find set-inclusion maximal solutions with respect to the predicates that are true. By using this built-in option, we can compute all the stable models of \(\mathcal{A}\) in one execution.

\section{Evaluation}
To assess the efficiency of the proposed method, we compared it with the state-of-the-art method PyBoolNet~\cite{klarner2017pyboolnet}.
We used a set of real-world Boolean models lying in various scales obtained from the literature.
These models are quite big (in size), complex (i.e., having high average in-degree, which is related to the number of prime-implicants) and most of them have never been fully analyzed.
We then applied the proposed method and PyBoolNet to computing minimal trap spaces of these real-world models.
It is notable that unlike existing analysis shown in the literature, we did not fix specific values for source nodes (i.e., some node \(v\) such that \(f_v = v\)) in these models. 
To solve the ASP problems, we used the same ASP solver CLINGO~\cite{DBLP:journals/aicom/GebserKKOSS11} and the same configuration as that used in PyBoolNet~\cite{klarner2015computing}.
Specifically, we used the configuration \texttt{--dom-pref=32, --heu=domain, --dom-mod=7} (subset maximality). We ran all the benchmarks on a virtual machine whose environment is CPU: Intel(R) Core(TM) i7-3630QM 2.40GHz x 4, Memory: 8 GB, Ubuntu 18.04.2 64 bit. Finally, we set a time limit as one hour for each model.

% \sylvain{we need a source for the models as much as possible, or to refer to some place where people can access them to reproduce the benchmark.}
% \vangiang{Yes. I have added reference sources for the models but some models are still missing now.}

@@

The first observation is that the proposed method much outperforms PyBoolNet in computational time. More specifically, ...
\vangiang{In the journal version, we can measure the memory consumption of the two methods}

The second observation is that ...

\begin{table}[!ht]
  \caption{Timing comparisons between the proposed method and PyBoolNet on the selected real-world models.
    Columns "\(n\)", "\(e\)", and "\(s\)" denote the numbers of nodes, interactions, and source nodes of each model, respectively. For each method, Column "\(|M|\)" denotes the number of minimal trap spaces and Column "time (s)" denotes the computation time in seconds.
    "DNF" means that the method did not finish the computation within one hour.}
  \centering
  \label{tab:result_real}
  \begin{tabular}{lrrrrrrr}
    \toprule
    & & & & \multicolumn{2}{c}{PyBoolNet} & \multicolumn{2}{c}{Proposed method}\\
    \cmidrule(lr){5-6}\cmidrule(lr){7-8}
    model & $n$ & $e$ & $s$ & $|M|$ & time (s) & $|M|$ & time (s) \\ \midrule
    inflammatory-bowel-disease~\cite{DBLP:journals/bmcsb/HelikarKMBRMWSLR12} & 47 & 287 & 0 & DNF & DNF & 1 & 296.23 \\
    T-LGL-survival-network-2008~\cite{DBLP:journals/bmcsb/HelikarKMBRMWSLR12} & 61 & 193 & 7 & - & - & 318 & 0.24 \\
    butanol-production~\cite{DBLP:journals/bmcsb/HelikarKMBRMWSLR12} & 66 & 139 & 13 & - & - & 512 & 0.17 \\
    colitis-associated-colon-cancer~\cite{DBLP:journals/bmcsb/HelikarKMBRMWSLR12} & 70 & 153 & 1 & - & - & 10 & 0.18 \\
    IL-6-signalling~\cite{DBLP:journals/bmcsb/HelikarKMBRMWSLR12} & 86 & 149 & 15 & - & - & 512 & 0.32 \\
    Corral-ThIL-17-diff~\cite{corral2021interplay} & 92 & 246 & 16 & - & - & 5724 & 0.90 \\
    Korkut-2015~\cite{lee2019signal} & 99 & - & 12 & DNF & DNF & 2060 & 2.86 \\ \midrule

    adhesion-cip-migration-cell-cycle~\cite{guberman2020boolean} & 121 & 493 & 4 & - & - & 78 & 3.72 \\
    interferon-1~\cite{ostaszewski2021covid19} & 121 & 190 & 55 & - & - & 512 & 0.43 \\
    TCR-TLR5-signaling-2018~\cite{rodriguez2019cooperation} & 130 & 273 & 2 & - & - & 48 & 0.50 \\
    influenza-virus-replication-cycle~\cite{DBLP:journals/bmcsb/HelikarKMBRMWSLR12} & 131 & 302 & 11 & - & - & 2560 & 1.07 \\
    signaling-in-prostate-cancer~\cite{Montagud2021} & 133 & 431 & 0 & - & - & 812 & 1.40 \\
    HIV-1-with-T-cell-signaling~\cite{DBLP:journals/bmcsb/HelikarKMBRMWSLR12} & 138 & 368 & 14 & DNF & DNF & 1408 & 1.44 \\
    signal-transduction-in-fibroblasts~\cite{helikar2008emergent} & 139 & 557 & 9 & - & - & 375850 & 331.87 \\
    HMOX-1-pathway~\cite{ostaszewski2021covid19} & 145 & 228 & 56 & - & - & 5120 & 0.99 \\
    kynurenine-pathway~\cite{ostaszewski2021covid19} & 150 & 304 & 72 & - & - & 512 & 3.79 \\
    virus-replication-cycle~\cite{ostaszewski2021covid19} & 154 & 268 & 25 & - & - & 1024 & 0.67 \\
    immune-system~\cite{DBLP:journals/bmcsb/HelikarKMBRMWSLR12} & 164 & 506 & 13 & DNF & DNF & 36852 & 14.19 \\
    er-stress~\cite{ostaszewski2021covid19} & 182 & 266 & 75 & - & - & 25600 & 4.54 \\
    cascade-3~\cite{Tsirvouli2020} & 183 & 603 & 0 & - & - & 1 & 1.65 \\
    CHO-2016~\cite{lee2019signal} & 200 & 696 & 13 & - & - & 1024 & 2.10 \\ \midrule
